Paper Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-03-15 Initial-paper/paper.tex
put todo list in readme file and created a setup for the paper itself

@@

\begin{itemize}
	\item Introduce planning problem
	\item Introduce planning for uncertainty
	\item Introduce the problem definition and motivation
\end{itemize}

We will focus on 2 of the current state of the art probabilistic planning
algorithms that apply determinization in probabilistic domains and criticize
the approaches by formulating a real-world domain as opposed to the IPPC
domains.  By comparing both approaches and analyzing other state of the art
work we will propose some adjustments which we will theoretically test in this
domain. If it is realistic, we will also try to create an empirical evaluation.

@@

\section{Related Work}

\begin{itemize}
	\item Introduce the previously read papers
	\item Introduce the current state of the art papers that use deterministic approaches for probablistic domains deadling with uncertainty
\end{itemize}

>>>>

\begin{abstract}
blabla
\end{abstract}

@@

\begin{itemize}
	\item Describe probabilistic planning problem
	\item Introduce planning for uncertainty
	\item Describe how deterministic classical planners can be used in probabilistic domains and motivate why this is interesting
	\item Introduce the qualities of replanning and the second planning algorithm
	\item Describe the need for a new domain for real world applications
	\item Describe the goal and tools used to reach this goal
\end{itemize}

@@

\section{Related Work}
% Use related work to display the differences with own work

\begin{itemize}
	\item Discuss the related work and how their approaches are different
	\item Discuss the other domains and why our domain adds anything to the community
	\item Introduce the current state of the art papers that use deterministic approaches for probablistic domains deadling with uncertainty
\end{itemize}
